Integration of Multiple Constraints in ACG

### 2013-09-22 lenls/paper.tex
LENLS: Fixed the affiliations
LENLS: Implemented style remarks

\mainmatter              % start of the contributions
%
\title{Integration of Multiple Constraints in ACG}
%
\titlerunning{Constraints in ACG}  % abbreviated title (for running head)
%                                    also used for the TOC unless
%                                    \toctitle is used
%
\author{Jiří Maršík\inst{1,2} \and Maxime Amblard\inst{1,2}}
%
\authorrunning{Maršík et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Jiří Maršík and Maxime Amblard}
%
\institute{Université de Lorraine, LORIA, Nancy, 54000, France\\
\email{\{jiri.marsik, maxime.amblard\}@loria.fr},\\
\and
INRIA, Nancy, 54000, France}

@@

We begin with a short review of Abstract Categorial Grammars in which we
highlight the ways in which Abstract Categorial Grammars facilitate
decomposition of linguistic description. We follow that by a closer look at an
example linguistic constraint and how its treatment might look like in a
categorial grammar, which motivates our proposed extension. We then present
the Graphical Abstract Categorial Grammars and discuss some of its formal
properties. We then finish with an illustration of our approach which
incorporates linguistic contribution from multiple sources into a single
coherent and simple grammar and discuss the limitations and challenges of
adopting this approach.

@@

We first review the grammatical framework in which we conduct our
work. Abstract Categorial Grammars are built upon two mathematical structures,
\emph{(higher-order) signatures} and \emph{lexicons}.

@@

The most common pattern will have us using two object signatures for the
surface forms of utterances (strings) and their logical forms (logical
propositions) and an abstract signature which is connected to both of the
object signatures via lexicons (as we can see in
Figure~\ref{fig:acg-comp-basic}). Parsing is then just a matter of inverting
the surface lexicon to get the abstract term and then applying to it the
logical lexicon. Generation is symmetric, we simply invert the logical lexicon
and apply the surface lexicon.

@@

The first constitutes the Constraint pattern used throughout
\cite{pogodalla2012controlling}. Imagine we want our grammar to enforce a
particular linguistic constraint, say that tensed clauses form islands for
quantifier scope, and suppose we want to proceed by refining our types so as
to make linguistic structures violating the constraint untypable. We could
dive in to our grammar and rewrite it to use the new types. However, we can
also keep the existing grammar intact and complement it with a signature and a
lexicon that translates that signature to the abstract-most signature of our
existing grammar. Usually, the new signature will resemble the prior
abstract-most one, albeit with more fine-grained types necessary to express
the constraint in question.

>>>>

\mainmatter              % start of the contributions
%
\title{Integration of Multiple Constraints in ACG}
%
\titlerunning{Constraints in ACG}  % abbreviated title (for running head)
%                                    also used for the TOC unless
%                                    \toctitle is used
%
\author{Jiří Maršík\inst{1,2,3} \and Maxime Amblard\inst{1,2,3}}
%
\authorrunning{Maršík et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Jiří Maršík and Maxime Amblard}
%
\institute{Université de Lorraine, Laboratoire lorrain de recherche en informatique et ses applications, UMR 7503, Vandoeuvre-lès-Nancy, 54500, France\\
\email{\{jiri.marsik, maxime.amblard\}@loria.fr},\\
\and
INRIA, Villers-lès-Nancy, 54600, France\\
\and
CNRS, Loria, Vandoeuvre-lès-Nancy, UMR 7503, 54500, France}

@@

We begin with a short review of Abstract Categorial Grammars where we
highlight the ways in which Abstract Categorial Grammars facilitate
decomposition of linguistic description. We follow that by a closer look at an
example of a linguistic constraint. This discussion motivates our proposed
extension. We then present the Graphical Abstract Categorial Grammars and
consider some of its formal properties. We then finish with an illustration of
our approach which incorporates linguistic contribution from multiple sources
into a single coherent and simple grammar and examine the limitations and
challenges of adopting this approach.

@@

We first review the grammatical framework in which we conduct our
work. Abstract Categorial Grammars are built upon two mathematical structures:
\emph{(higher-order) signatures} and \emph{lexicons}.

@@

The most common pattern will have us using two object signatures,
$\Sigma_{String}$ and $\Sigma_{Sem}$, for the surface forms of utterances
(strings) and their logical forms (logical propositions) and an abstract
signature, $\Sigma_{Synt}$, which is connected to both of the object
signatures via lexicons (as we can see in
Figure~\ref{fig:acg-comp-basic}). Parsing is then just a matter of inverting
the surface lexicon to get the abstract term and then applying to it the
logical lexicon. Generation is symmetric, we simply invert the logical lexicon
and apply the surface lexicon.

@@

The first constitutes the Constraint pattern used throughout
\cite{pogodalla2012controlling}. Imagine we want our grammar to enforce a
particular linguistic constraint, say that tensed clauses form islands for
quantifier scope, and suppose we want to proceed by refining our types so as
to make linguistic structures violating the constraint untypable. We could
dive into our grammar and rewrite it to use the new types. However, we can
also keep the existing grammar intact and complement it with a signature and a
lexicon that translates that signature to the abstract-most signature of our
existing grammar. Usually, the new signature will resemble the prior
abstract-most one, albeit with more fine-grained types necessary to express
the constraint in question.
